(Working Title) Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-03 ms.tex
First half of intro

\title{(Working Title) Properties of the \KT\ Campaign 1 Planets, 
False Positive Probabilities, and Confirmation of $N$ Systems. You 
Were Warned: it's a Working Title.}

\author{
% The Heavy Lifters
Benjamin T. Montet\altaffilmark{1,2}, 
Daniel Foreman-Mackey\altaffilmark{3},
Timothy D. Morton,
% The Benefactors
John Asher Johnson,
David W. Hogg,
% The Observers, as PIs 
% (ranked by integration time x collecting area)
Brendan P. Bowler,
David W. Latham,
Andrew W. Mann,
% The observers, as a group
And Whoever DaveL Tells Us to Add as TRES Team Members
}

@@

\begin{abstract}
\btmtodo{This is where the abstract will go}
Of the 36 planet candidates presented in \paperit{} we confirm 
\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
at the \btmtodo{confidence} level. Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
orbital period of 33 days.
\end{abstract}

@@

\section{Introduction}

>>>>

\title{(Working Title) Stellar and Planetary Properties of \KT\ Campaign 1
Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving 
Earth-like Insolation?)}

\author{
% The Heavy Lifters
Benjamin T. Montet\altaffilmark{1,2}, 
Daniel Foreman-Mackey\altaffilmark{3},
Timothy D. Morton,
% The Benefactors
John Asher Johnson,
David W. Hogg,
% The Observers
% (ranked by integration time x collecting area)
Brendan P. Bowler,
David W. Latham,
Allyson Bieryla,
Andrew W. Mann,
And Any TRES Team Members We Should Add
}

@@

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ Campaign 1. 
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm 
\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
at the \btmtodo{confidence} level.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
orbital period of 33 days.
\anytodo{Anything we should add?}
\end{abstract}

@@

\section{Introduction}
The \kep\ telescope \citep{Borucki10} has led to a revolution in stellar and planetary 
astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
The demise of two reaction wheels on the spacecraft led to a repurposing 
of the spacecraft into the \KT\ mission, in which the telescope points at
fields near the ecliptic plane for $\sim 75$ days at a time \citep{Howell14}.
In this observing strategy, two axes of motion of the spacecraft are 
controlled by the two remaining reaction wheels, while the roll of the 
spacecraft is balanced with solar radiation pressure and quasiperiodic 
thruster firing.
The result of this observing strategy is that the targets appear to drift
at the rate of $\sim 1\arcsec$ s$^{-1}$, with rapid corrections that occur
approximately once every six hours.
Over the full duration of each campaign, the targets appear to remain at 
approximately the same location on the detector.
Both the slow drift and the corrections are observable by eye, and by viewing the
motions of each star \citep{Barentsen15} it is apparent that \KT\ is working as 
advertised.
Therefore, apertures can be defined around each star and aperture photometry can be
defined in the usual way.

\KT\ light curves produced with aperture photometry contain substantial pointing-induced
photometric variations caused by the star's apparent motion over a poorly-defined flat 
field. 
Worse yet, these variations occur on timescales similar to transit signals, potentially
masking the observational signature of a planet passing between \kep\ and the host star.

There has been considerable effort to recover these signals.
\citet{Vanderburg14} extract aperture photometry and decorrelate with image centroid
position, ``correcting'' the data to ``remove'' the effects of the spacecraft motion.
These data were used to confirm the first planet discovered in \KT\ \citep{Vanderburg15}.
A similar technique was employed by \citet{Armstrong15a} to identify potential eclipsing
binary systems and to identify a transiting system very near a 3:2 period commensurability
\citep{Armstrong15b}.
\citet{Aigrain15} and \citet{Crossfield15} use a Gaussian Process model for the measured
flux, with pointing measurements as the inputs, and then “detrend” the data with that model.
The latter of these detected the first multi-planet system in \KT\ data.

What is common to all of these methods are that removal of systematics is considered a 
step to be undertaken before the search for planets. 
Under this strategy, it is implicitly assumed that the systematics are removed perfectly,
while retaining all of the astrophysical signal. 
Of course, it is impossible to perfectly separate the astrophysical and instrumental 
signal, and such a technique is prone to either over-fitting, in which some of the 
astrophysical signal is also removed, or under-fitting, in which some instrumental noise
remains.
A better strategy is to simultaneously fit both the signal and the noise, as is commonly
done in cosmology and, increasingly, in radial velocity searches for planetary systems
\citep[e.g.][]{Ferreira00, Boisse11, Haywood14, Grunblatt15}.

\paperit{} apply an altern
